FinalManuscript_DISCS_UG

### 2018-06-26 parts/03_methodology.tex
Polished methodology summary

We now recap the research questions and the corresponding methodology.
\begin{itemize}
	\item \textbf{Applicablity of homomorphic encryption algorithms for the use of image processing operations on encrypted data?} This will be addressed by the implementation of OpenCV library, and the evaluation of image quality (MSE, PSNR, SSIM).
	\item \textbf{Time efficiency in applying image manipulation operations.} This will be addressed by the implementation of OpenCV library, and the comparison of recorded processing time for image processing operations.
	\item \textbf{Security under differential and entropy attacks.}
	This will be addressed by the evaluation of security benchmarks for image encryption schemes (entropy analysis, correlation coefficient analysis, NPCR, UACI).
\end{itemize}

>>>>

In summary, the study will consist of
\begin{itemize}
	\item An implementation of an OpenCV library which implements homomorphic cryptosystems by Ziad, et al. \cite{ziad_cryptoimg:_2016}, Li, et al. \cite{li_elliptic_2012} and Smart and Vercauteren \cite{hutchison_fully_2010}.
	\item An implementation of image processing operations (intensity transformations, spatial filters) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, and cryptographic security, using standard test images from \cite{gonzalez_image_nodate}.
\end{itemize}

These will be conducted over the course of the first semester of AY 2018-2019 to allow for analysis of the results and paper preparation in the second semester. Additional cryptosystems, image operations, and cryptographic security tests may be included in the scope of the study, depending on future research.

We now provide a summary of how each of our reserch questions are addressed by the methodology.
\begin{itemize}
	\item \textbf{Applicablity of homomorphic encryption algorithms for the use of image processing operations on encrypted data?} This will be addressed by the implementation of OpenCV library, and the evaluation of image quality (MSE, PSNR, SSIM).
	\item \textbf{Time efficiency in applying image manipulation operations.} This will be addressed by the implementation of OpenCV library, and the comparison of recorded processing time for image processing operations.
	\item \textbf{Security under differential and entropy attacks.}
	This will be addressed by the evaluation of security benchmarks for image encryption schemes (entropy analysis, correlation coefficient analysis, NPCR, UACI).
\end{itemize}
